### 2020-01-06 Literature Review/Literature Review - Revised/.history/sections/MARL_20200106140400.tex
Updated Game Dynamics

>>>>

\section{Game Dynamics}

Game Dynamics (which I often refer to as Multi Agent Dynamics or Learning Dynamics) considers the
problem of mathematically modelling Multi Agent Systems who adapt through repeated interact with one
another. This model then serves to be able to predict the evolution of the system as well as to
understand the trajectory of learning. Typically, this looks at considering whether or not the
method is likely to converge towards a Nash equilibrium. This is generally a difficult problem to
solve \cite{ShohamMultiagentFoundations} for all but toy problems. To extend this applicability into
real world settings requires the study of stable equilbrium points;
\cite{Letcher2019DifferentiableMechanics} shows that the stable equilbrium and Nash equilibrium (NE)
are not necessarily the same and, in fact, argue that stable points are more informative than NEs.
Stability provides some guarantees against the stochastic nature of the environment since a stable
equilibrium will always be returned to even after perturbations. This extremely important in Safe
and Trusted AI as it provides guarantees against undesired behaviour in real world environments.

\TODO{Add in the papers from Mendeley which are useful to this part of the study}
